Fail Faster

### 2025-03-19 paper/paper.tex
delete subsection about the trick, nobody cares

\subsubsection{The Trick at Other Types}
To write more interesting generators, we also need the ability to generate code that manipulates run-time values.
For instance, consider this generator

\jwc{need a better example here}

\begin{figure}
\begin{lstlisting}
let int_or_zero : int Bq.t =
  let%bind n = size in
  if n <= 5 then return 0 else Bq.int

let split_bool (b : bool code) : bool Gen.t =
  fun _ _ ->  _

\end{lstlisting}
\caption{??}
\label{fig:trick-example}
\end{figure}

\jwc{Describe split --- this section is approximately experts-only, but you can just point at the Andras paper and the things it cites.}

>>>>

% \subsubsection{The Trick at Other Types}
% To write more interesting generators, we also need the ability to generate code that manipulates run-time values.
% For instance, consider this generator

% \jwc{need a better example here}

% \begin{figure}
% \begin{lstlisting}
% let int_or_zero : int Bq.t =
%   let%bind n = size in
%   if n <= 5 then return 0 else Bq.int

% let split_bool (b : bool code) : bool Gen.t =
%   fun _ _ ->  _

% \end{lstlisting}
% \caption{??}
% \label{fig:trick-example}
% \end{figure}

% \jwc{Describe split --- this section is approximately experts-only, but you can just point at the Andras paper and the things it cites.}
